---
title: "Survival Analysis"
author: "Bramack"
date: "2024-06-21"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# load packages
library(tidyverse)
library(here)
library(survival)
library(survminer)
```{r}
```
# read data

data<-read.csv(here("rdata folder","survdatao.csv"))
```{r}
```
# print the first few rows of the data

head(data)
```{r}
```

#convert data columns to data type
data$DOB<-as.Date(data$DOB,format="%Y-%m-%d")
data$StartArtDate<-as.Date(data$S.ART.D,format="%Y-%m-%D")
data$Dateconfirmedhivpositive<-as.Date(data$D.C.HIV.P,format="%Y-%m-%d")
data$dispense_date<-as.Date(data$DispenseDate,format="%Y-%m-%d")
data$exit_date<-as.Date(data$ExitDate,format="%Y-%m-%D")
```{r}
```

# Ensure data is correctly formatted
str(data)
```{r}
```
#create time and status variable for survival analysis
data$time<-as.numeric(difftime(data$ExitDate,data$S.ART.D,units="days"))
data$status<-ifelse(is.na(data$ExitDate),0,1)

```{r}
```

#print the first few rows to check the new column
head(data)
```{r}
```

# create a survival object
surv_object<-Surv(time=data$time,event=data$status)

```{r}
```

#Fit a kaplan meier survival curve
fit<-survfit(surv_object~1,data=data)
```{r}
```
#print the summary of the fit
summary(fit)

```{r}
```
#plot the survival curve
ggsurvplot(fit,data=data,xlab="Time(days)",ylab="survival probability",
           title="Kaplan Meier Survival Curve",
           ggtheme=theme_minimal())

```{r}
```
# plot visualisation
Img<-read_png("survplot.png")

```{r}
